### 2022-03-15 paper3.tex
3 article summaries
finish contributions and future directions
Finish paper 2 revisions

\hypertarget{paper-3}{%
\chapter{Social Norms under Uncertain Times: A dynamic study of Stay-At-Home and Vaccination Rates During the Covid-19 Pandemic}\label{paper-3}}

@@

This paper examines how social norms are formed under conditions of uncertainty
using the case studies of stay-at-home and vaccination rates during the Covid-19
pandemic. I test fear-based models of behavioral adaption to public health
recommendations as well as patterns of complex social contagion using linear
mixed effects models. These models show that complex contagion is a valid
framework for the social contagion of new norms during Covid-19. However, I find
important moderating effect of signal discordance, the contextual diversity of
signals received by an ego.

% need to explain a little bit more what diversity of signals etc means (since this is the first look)

@@

A second strategy pushed by the CDC, once available, was to receive vaccination
to prevent the effects of the Covid-19 virus if infected. Vaccinations like
Pfizer-BioNTech (Comirnaty, tozinameran, BNT162b2), and Janssen/Johnson \&
Johnson, Moderna (mRNA-1273) started receiving approval for emergency use
authorization by the United States Food and Drug Administration (FDA) in
December 2020.

@@

There is little research on stay-at-home rates, especially in cases of pandemics
or disasters. Though research on the causes of population mobility did expand
after the onset of the Covid-19 pandemic 
\citep{bargainTrustCompliancePublic2020, bourassaStatelevelStayathomeOrders2020, bourassaSocialDistancingHealth2020, grossmanPoliticalPartisanshipInfluences2020, haggerPredictingSocialDistancing2020, hillBloodChristCompels2020, hillNastiestQuestion, hillLoveThyAged2021,huynhDoesCultureMatter2020}, most research focused on unchanging cultural
determinants of the reduction in stay-at-home rates. For instance, \citet{gibbons_etal21}
 finds that social capital had spatially inconsistent effects on
stay-at-home rates. Instead of focusing on cultural relationships with
stay-at-home rates, this paper will instead focus on the dynamic nature of
population mobility across population networks.

@@

This article researches the formation of social norms governing health behaviors
in cases of extreme uncertainty during the Covid-19 pandemic. Using theories of complex
contagion, associative diffusion and the integrated theoretical framework of
norms, I test how these health behaviors are outcomes of contagion and
discordance of signals, as well as other factors affecting associations like
religious and political conservatism, attention to television media sources,
and online norms as measured by information-search behaviors. Before outlining
my central hypotheses, I offer an overview of the current state of the social
contagion literature. After that, I will outline how I compiled this unique
longitudinal data set from Google, the CDC, Facebook and other sources and how I
define and calculate signal and discordance, two key independent variables for
this paper. To model stay-at-home and vaccination rates, I use linear mixed effects
models with random effects as a longitudinal model of contagion. After
interpreting the results of the models, I discuss the implications of these
findings for the sociological understanding of social contagion and the
formation of social norms.

@@

While much of the social contagion literature, like the theories above, focuses
on structural boundaries and homophily as causes of how diffusion occurs,
\citet{goldbergSocialContagionAssociative2018} propose a
disrupting alternative mechanism. They argue that what actually diffuses during
social contagion are the perceptions about which beliefs or behaviors are
compatible with one another, what they call ``associative diffusion.'' This
argument that culture does not spread like a virus but instead is dependent on
how belief structures are connected to each other is important to test because
norms around health behaviors became politicized issues during the Covid-19
pandemic. This means that the stay-at-home or vaccination behavior themselves
were not contagious, but the cognitive association of precisely what social
distancing or vaccination uptake \emph{meant} were spreading between populations of
individuals. Moreover, as \citet{houghton20} outlines, diffusants - the things that are
diffusing through a population, are not independent of each other \citep{mason_etal07}. When we take into account the interdependence between different beliefs that are diffusing, such as Covid-19 is a hoax, social distancing saves
lives, the Covid-19 vaccine includes a microchip to control your thoughts, and lockdown
is against the rights guaranteed in the US constitution, we can imagine how
these various diffusants become associated together into structures of belief
through schemas of perception \citep{houghton20}. While this cognitive theory of cultural variation is difficult to test, the theory it supplies provides a solid framework for how behavioral norms formed during the pandemic.

@@

\hypertarget{covid-19-case-rates}{%
\subsubsection{Covid-19 Case Rates}\label{covid-19-case-rates}}

To estimate the concept of `real threat of infection' for a fear-based model of
health behaviors, the models use county-level Covid-19 case rates with
data compiled by The New York Times \citeyearpar{covid_data}. It is widely acknowledged that there are biases in this data due to inconsistencies and availability in testing as well as
different community propensity to test \citep{gu22, cdc20a}. However, it is the best
measure we have of actual case rates. County data are scaled with a rolling mean
with a rolling window width of seven days to smooth out intra-week noise. Case
Rate is measured as number of cases per 100,000 population. Observations vary
from a minimum of 0 to a maximum of 1,565 across the two datasets.

@@

To operationalize the search for online norms, I use Google search trends \citep{googletrends},
over the study period across individual designated media markets areas (DMAs), a
nonoverlapping aggregation of U.S. counties to 210 media markets based on
similar population clusters \citep{dma_key}. To investigate the rate of \emph{searching} for norms
online in both cases, I use the following search topics: `Social Distancing'
(2020, stay-at-home case only), `Covid-19 Vaccine' (2021, vaccination uptake case
only) and Covid Conspiracy (2020-2021, both cases). Search topics are a more
robust measurement than a single search term: topics are aggregations of the
rates of multiple, highly correlated search terms together into a cohesive
topic. For example, while `Beyoncé,' `Beyonce' and `beyonce knowles' are all
separate search terms, `Beyoncé Knowles' encompasses all of these into a single
search topic. While the data is originally on a scale of 0 to 100, with
100 being the maximum search popularity out of all DMAs, Google Search Trend are
now only available cross-sectionally (a single time period across a geography)
or time-series (a single geo-location across time). To remedy this and build a
longitudinal dataset of each search topic, I follow the method proposed in \citet[p. 5]{park_etal}.
This method involves building a dataset of unscaled
cross-sectional values, selecting a DMA to use to establish the rescaling ratio
(I use `Los Angeles CA'), and then finding the time-series values for the one
DMA. To find the rescaling ratio for each week in the time-series, you divide
the time-series value for each week by the cross-sectional value for each week,
resulting in a rescaling vector to be used for all weeks in the dataset across
geographies. To rescale each longitudinal value, multiply the respective week's
rescaling ratio by the cross-sectional value. Rescaled longitudinal data was
compared against time-series data for multiple test counties and was equivalent.
For a more in-depth explanation of this procedure, see \citet[p. 5]{park_etal}.

@@

In Table \ref{tab:google-tab} and Figures \ref{fig:plot-google-h2} -
\ref{fig:plot-google-h3}, I present the elaboratory county-level models that
predict stay-at-home rates, or, time spent in residence. Model 1 addresses
hypothesis 1, that relatively higher local rates of infection will lead to
increased time spent in residence. This model's phi paramter is 0.933, which is
a good indicator that adjacent time points for each county are related and the
model is specified correctly (Finch, Bolin, and Kelley 2014). In this first model, many controls
have an impact on the outcome. For instance, when controlling for everything
else, the percent of GOP votes in 2016, the percentage of residents who identify
racially as White, and higher rates of unemployment increased the stay-at-home
rate while Searches for norms online seems to
have an effect on the outcome: searches for `Fox News' are associated with
decreased stay-at-home rates, while searching for both `Social Distancing' and
`Covid Conspiracy' tend to increase time spent in residence. Interestingly, the
perceived threat of the virus, measured through Covid-19 case rates, were not
significantly related to stay-at-home rates in model 1. In other words, for
every 1 standard deviation increase in Covid-19 case rates, stay-at-home rates
actually decreased by
0.0003 (\emph{p} = 0.936),
a very small and insignificant effect. In this case, I fail to reject the null
hypothesis that relatively higher local rates of infection will lead to
increased time spent in residence.

@@

However, this coefficient is inadequate alone because the effect varies over
time; the interaction between week and movement signal is negative, meaning that
week partially moderates the effect of the signal. Figure
\ref{fig:plot-google-h2} illustrates this interaction. In the early days of the
Covid-19 pandemic, seeing a high rate of time spent in residence by alters led
to a high rate of staying-at-home for county egos. However, as the pandemic
progressed, these signals switched. In other words, towards the end of 2020,
other factors may have come into play and if a county saw its' alters social
distancing and spending time in residence, ego counties spent less time at home.
Theoretically, this may be because individuals saw their adjacent communities
with strong public health norms and felt safe and justified their own deviance.
However, if an ego county received signals that
others were failing to social distance, they were more likely to stay-at-home.
In this case, the threat of the virus may have been more evident for
individuals.

@@

In Table \ref{tab:vacc-tab} and Figures \ref{fig:plot-vacc-h2} -
\ref{fig:plot-vacc-h3}, I present the elaboratory county-level models that
predict vaccination uptake rates. The parameter phi in model 1 is .985, which is
a good indicator that adjacent time points for each county are related and this
is an appropriate modeling technique for the data \citep{finch_etal14}. Table
\ref{tab:vacc-tab} Model 1 addresses hypothesis 1, that relatively higher local
rates of infection will lead to increased vaccination uptake. In this first
model, we see various controls impacting vaccination rates. For instance, when
controlling for everything else, higher income areas lead to higher vaccination
uptake. On the other hand, counties with higher unemployment and higher votes
for Donald J. Trump in the 2020 election are associated with lower vaccination
rates. Interestingly, counties that search for Fox News are more likely to have
higher vaccination rates while those performing Google searches for information
about the vaccine are likely to have lower rates of vaccination. The test of
Hypothesis 1 also returns surprising results: every 1 standard deviation
increase in county Covid-19 case rates is expected to yield a -0.008 decrease in vaccination rates. This may be due to time ordering or reverse
causality, where individuals in counties who have higher rates of vaccination
are less likely to take tests to Covid-19 infections because of the higher
likelihood of asymptomaticity. However, it is important to note that the Case
Rate variable actually becomes distorted with the addition of Vaccination Signal
and Vaccination Discordance in models 2 and 3. Distortion occurs when the
direction of a focal relationship reverses sign once a third (distorter)
variable is controlled, in this case, those related to signal. Therefore, the
results of hypothesis 1 are quite inconclusive.

@@

This paper examines how social norms are formed under conditions of uncertainty
using the case studies of stay-at-home rates and vaccination rates during the
Covid-19 pandemic. I test fear-based models of behavioral adaption to public
health recommendations as well as patterns of complex social contagion. This
article demonstrates that the establishment of social norms under patterns of
uncertainty in my two cases do follow the theorized framework of complex
contagion; however, I find a moderating effect of signal discordance to be an
overlooked factor in theories of contagion.

@@

This article also provides a new adaption of the theory of complex contagion
using big data from the natural experiment of Covid-19. Because most studies of
complex contagion utilize agent-based modeling or studies of social media \citep{aralExerciseContagionGlobal2017,sprague_house17,bond_etal12,latane_etal94}, combining measures of actual behavioral outcomes with data from
social media websites provides a further test of ecological and external
validity for the theory.

>>>>

\hypertarget{paper-3}{%
\chapter{Social Norms under Uncertain Times: A dynamic study of Stay-At-Home and Vaccination Rates During the COVID-19 Pandemic}\label{paper-3}}

@@

This paper examines how social norms are formed under conditions of uncertainty
using the case studies of stay-at-home and vaccination rates during the COVID-19
pandemic. I test fear-based models of behavioral adaption to public health
recommendations as well as patterns of complex social contagion using linear
mixed effects models. These models show that complex contagion is a valid
framework for the social contagion of new norms during COVID-19. However, I find
important moderating effect of signal discordance, the contextual diversity of
signals received by an ego.

% need to explain a little bit more what diversity of signals etc means (since this is the first look) 
% what else needs to be said here to properly convey the importance and impact of this finding?

@@

A second strategy pushed by the CDC, once available, was to receive vaccination
to prevent the effects of the COVID-19 virus if infected. Vaccinations like
Pfizer-BioNTech (Comirnaty, tozinameran, BNT162b2), and Janssen/Johnson \&
Johnson, Moderna (mRNA-1273) started receiving approval for emergency use
authorization by the United States Food and Drug Administration (FDA) in
December 2020.

@@

There is little research on stay-at-home rates, especially in cases of pandemics
or disasters. Though research on the causes of population mobility did expand
after the onset of the COVID-19 pandemic 
\citep{bargainTrustCompliancePublic2020, bourassaStatelevelStayathomeOrders2020, bourassaSocialDistancingHealth2020, grossmanPoliticalPartisanshipInfluences2020, haggerPredictingSocialDistancing2020, hillBloodChristCompels2020, hillNastiestQuestion, hillLoveThyAged2021,huynhDoesCultureMatter2020}, most research focused on unchanging cultural
determinants of the reduction in stay-at-home rates. For instance, \citet{gibbons_etal21}
 finds that social capital had spatially inconsistent effects on
stay-at-home rates. Instead of focusing on cultural relationships with
stay-at-home rates, this paper will instead focus on the dynamic nature of
population mobility across population networks.

@@

This article researches the formation of social norms governing health behaviors
in cases of extreme uncertainty during the COVID-19 pandemic. Using theories of complex
contagion, associative diffusion and the integrated theoretical framework of
norms, I test how these health behaviors are outcomes of contagion and
discordance of signals, as well as other factors affecting associations like
religious and political conservatism, attention to television media sources,
and online norms as measured by information-search behaviors. Before outlining
my central hypotheses, I offer an overview of the current state of the social
contagion literature. After that, I will outline how I compiled this unique
longitudinal data set from Google, the CDC, Facebook and other sources and how I
define and calculate signal and discordance, two key independent variables for
this paper. To model stay-at-home and vaccination rates, I use linear mixed effects
models with random effects as a longitudinal model of contagion. After
interpreting the results of the models, I discuss the implications of these
findings for the sociological understanding of social contagion and the
formation of social norms.

@@

While much of the social contagion literature, like the theories above, focuses
on structural boundaries and homophily as causes of how diffusion occurs,
\citet{goldbergSocialContagionAssociative2018} propose a
disrupting alternative mechanism. They argue that what actually diffuses during
social contagion are the perceptions about which beliefs or behaviors are
compatible with one another, what they call ``associative diffusion.'' This
argument that culture does not spread like a virus but instead is dependent on
how belief structures are connected to each other is important to test because
norms around health behaviors became politicized issues during the COVID-19
pandemic. This means that the stay-at-home or vaccination behavior themselves
were not contagious, but the cognitive association of precisely what social
distancing or vaccination uptake \emph{meant} were spreading between populations of
individuals. Moreover, as \citet{houghton20} outlines, diffusants - the things that are
diffusing through a population, are not independent of each other \citep{mason_etal07}. When we take into account the interdependence between different beliefs that are diffusing, such as COVID-19 is a hoax, social distancing saves
lives, the COVID-19 vaccine includes a microchip to control your thoughts, and lockdown
is against the rights guaranteed in the US constitution, we can imagine how
these various diffusants become associated together into structures of belief
through schemas of perception \citep{houghton20}. While this cognitive theory of cultural variation is difficult to test, the theory it supplies provides a solid framework for how behavioral norms formed during the pandemic.

@@

\hypertarget{COVID-19-case-rates}{%
\subsubsection{COVID-19 Case Rates}\label{COVID-19-case-rates}}

To estimate the concept of `real threat of infection' for a fear-based model of
health behaviors, the models use county-level COVID-19 case rates with
data compiled by The New York Times \citeyearpar{covid_data}. It is widely acknowledged that there are biases in this data due to inconsistencies and availability in testing as well as
different community propensity to test \citep{gu22, cdc20a}. However, it is the best
measure we have of actual case rates. County data are scaled with a rolling mean
with a rolling window width of seven days to smooth out intra-week noise. Case
Rate is measured as number of cases per 100,000 population. Observations vary
from a minimum of 0 to a maximum of 1,565 across the two datasets.

@@

% TODO Mention that article-1 says that this can show interest (cite jungherr also) but does not show actions

To operationalize the search for online norms, I use Google search trends \citep{googletrends},
over the study period across individual designated media markets areas (DMAs), a
nonoverlapping aggregation of U.S. counties to 210 media markets based on
similar population clusters \citep{dma_key}. To investigate the rate of \emph{searching} for norms
online in both cases, I use the following search topics: `Social Distancing'
(2020, stay-at-home case only), `COVID-19 Vaccine' (2021, vaccination uptake case
only) and Covid Conspiracy (2020-2021, both cases). Search topics are a more
robust measurement than a single search term: topics are aggregations of the
rates of multiple, highly correlated search terms together into a cohesive
topic. For example, while `Beyoncé,' `Beyonce' and `beyonce knowles' are all
separate search terms, `Beyoncé Knowles' encompasses all of these into a single
search topic. While the data is originally on a scale of 0 to 100, with
100 being the maximum search popularity out of all DMAs, Google Search Trend are
now only available cross-sectionally (a single time period across a geography)
or time-series (a single geo-location across time). To remedy this and build a
longitudinal dataset of each search topic, I follow the method proposed in \citet[p. 5]{park_etal}.
This method involves building a dataset of unscaled
cross-sectional values, selecting a DMA to use to establish the rescaling ratio
(I use `Los Angeles CA'), and then finding the time-series values for the one
DMA. To find the rescaling ratio for each week in the time-series, you divide
the time-series value for each week by the cross-sectional value for each week,
resulting in a rescaling vector to be used for all weeks in the dataset across
geographies. To rescale each longitudinal value, multiply the respective week's
rescaling ratio by the cross-sectional value. Rescaled longitudinal data was
compared against time-series data for multiple test counties and was equivalent.
For a more in-depth explanation of this procedure, see \citet[p. 5]{park_etal}.

@@

In Table \ref{tab:google-tab} and Figures \ref{fig:plot-google-h2} -
\ref{fig:plot-google-h3}, I present the elaboratory county-level models that
predict stay-at-home rates, or, time spent in residence. Model 1 addresses
hypothesis 1, that relatively higher local rates of infection will lead to
increased time spent in residence. This model's phi paramter is 0.933, which is
a good indicator that adjacent time points for each county are related and the
model is specified correctly (Finch, Bolin, and Kelley 2014). In this first model, many controls
have an impact on the outcome. For instance, when controlling for everything
else, the percent of GOP votes in 2016, the percentage of residents who identify
racially as White, and higher rates of unemployment increased the stay-at-home
rate while Searches for norms online seems to
have an effect on the outcome: searches for `Fox News' are associated with
decreased stay-at-home rates, while searching for both `Social Distancing' and
`Covid Conspiracy' tend to increase time spent in residence. Interestingly, the
perceived threat of the virus, measured through COVID-19 case rates, were not
significantly related to stay-at-home rates in model 1. In other words, for
every 1 standard deviation increase in COVID-19 case rates, stay-at-home rates
actually decreased by
0.0003 (\emph{p} = 0.936),
a very small and insignificant effect. In this case, I fail to reject the null
hypothesis that relatively higher local rates of infection will lead to
increased time spent in residence.

@@

However, this coefficient is inadequate alone because the effect varies over
time; the interaction between week and movement signal is negative, meaning that
week partially moderates the effect of the signal. Figure
\ref{fig:plot-google-h2} illustrates this interaction. In the early days of the
COVID-19 pandemic, seeing a high rate of time spent in residence by alters led
to a high rate of staying-at-home for county egos. However, as the pandemic
progressed, these signals switched. In other words, towards the end of 2020,
other factors may have come into play and if a county saw its' alters social
distancing and spending time in residence, ego counties spent less time at home.
Theoretically, this may be because individuals saw their adjacent communities
with strong public health norms and felt safe and justified their own deviance.
However, if an ego county received signals that
others were failing to social distance, they were more likely to stay-at-home.
In this case, the threat of the virus may have been more evident for
individuals.

@@

In Table \ref{tab:vacc-tab} and Figures \ref{fig:plot-vacc-h2} -
\ref{fig:plot-vacc-h3}, I present the elaboratory county-level models that
predict vaccination uptake rates. The parameter phi in model 1 is .985, which is
a good indicator that adjacent time points for each county are related and this
is an appropriate modeling technique for the data \citep{finch_etal14}. Table
\ref{tab:vacc-tab} Model 1 addresses hypothesis 1, that relatively higher local
rates of infection will lead to increased vaccination uptake. In this first
model, we see various controls impacting vaccination rates. For instance, when
controlling for everything else, higher income areas lead to higher vaccination
uptake. On the other hand, counties with higher unemployment and higher votes
for Donald J. Trump in the 2020 election are associated with lower vaccination
rates. Interestingly, counties that search for Fox News are more likely to have
higher vaccination rates while those performing Google searches for information
about the vaccine are likely to have lower rates of vaccination. The test of
Hypothesis 1 also returns surprising results: every 1 standard deviation
increase in county COVID-19 case rates is expected to yield a -0.008 decrease in vaccination rates. This may be due to time ordering or reverse
causality, where individuals in counties who have higher rates of vaccination
are less likely to take tests to COVID-19 infections because of the higher
likelihood of asymptomaticity. However, it is important to note that the Case
Rate variable actually becomes distorted with the addition of Vaccination Signal
and Vaccination Discordance in models 2 and 3. Distortion occurs when the
direction of a focal relationship reverses sign once a third (distorter)
variable is controlled, in this case, those related to signal. Therefore, the
results of hypothesis 1 are quite inconclusive.

@@

This paper examines how social norms are formed under conditions of uncertainty
using the case studies of stay-at-home rates and vaccination rates during the
COVID-19 pandemic. I test fear-based models of behavioral adaption to public
health recommendations as well as patterns of complex social contagion. This
article demonstrates that the establishment of social norms under patterns of
uncertainty in my two cases do follow the theorized framework of complex
contagion; however, I find a moderating effect of signal discordance to be an
overlooked factor in theories of contagion.

@@

This article also provides a new adaption of the theory of complex contagion
using big data from the natural experiment of COVID-19. Because most studies of
complex contagion utilize agent-based modeling or studies of social media \citep{aralExerciseContagionGlobal2017,sprague_house17,bond_etal12,latane_etal94}, combining measures of actual behavioral outcomes with data from
social media websites provides a further test of ecological and external
validity for the theory.

### 2022-03-15 tables/paper2/table-model-2.tex
fix paper 1 tables, finish most of writing
Finish paper 2 revisions

\begin{table}[!h]

\caption{\label{tab:table-model-2}What predicts someone intentionally searched for information, by vehicle of information search}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llllll}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{5}{c}{Dependent Variable} \\
\cmidrule(l{3pt}r{3pt}){2-6}
  & Doctor & Person & Online Forum & Social Networking Site & Online Search\\
\midrule
\cellcolor{gray!6}{Received Info, Doctor} & \cellcolor{gray!6}{\num{1.942}***} & \cellcolor{gray!6}{\num{1.124}***} & \cellcolor{gray!6}{\num{0.181}} & \cellcolor{gray!6}{\num{0.540}**} & \cellcolor{gray!6}{\num{0.430}**}\\
Received Info, Person & \num{0.800}*** & \num{1.199}*** & \num{0.728}*** & \num{0.281} & \num{0.365}*\\
\cellcolor{gray!6}{Received Info, News} & \cellcolor{gray!6}{\num{0.437}**} & \cellcolor{gray!6}{\num{0.100}} & \cellcolor{gray!6}{\num{0.359}*} & \cellcolor{gray!6}{\num{0.514}*} & \cellcolor{gray!6}{\num{1.091}***}\\
Received Info, Social Networking Site & \num{-0.130} & \num{0.437}** & \num{-0.603}** & \num{0.731}*** & \num{1.272}***\\
\cellcolor{gray!6}{Received Info, Online Forum} & \cellcolor{gray!6}{\num{0.412}*} & \cellcolor{gray!6}{\num{0.263}+} & \cellcolor{gray!6}{\num{1.266}***} & \cellcolor{gray!6}{\num{0.974}***} & \cellcolor{gray!6}{\num{0.695}***}\\
Age & \num{0.002} & \num{0.001} & \num{-0.007} & \num{-0.003} & \num{0.029}***\\
\cellcolor{gray!6}{Associate's Deg or above} & \cellcolor{gray!6}{\num{0.542}**} & \cellcolor{gray!6}{\num{0.154}} & \cellcolor{gray!6}{\num{1.086}***} & \cellcolor{gray!6}{\num{1.344}***} & \cellcolor{gray!6}{\num{-0.952}***}\\
White & \num{0.631} & \num{0.245} & \num{0.009} & \num{0.559} & \num{0.012}\\
\cellcolor{gray!6}{Black} & \cellcolor{gray!6}{\num{0.366}} & \cellcolor{gray!6}{\num{0.208}} & \cellcolor{gray!6}{\num{0.608}} & \cellcolor{gray!6}{\num{0.646}} & \cellcolor{gray!6}{\num{0.357}}\\
Native American & \num{0.309} & \num{-0.696} & \num{0.209} & \num{0.762} & \num{-0.831}\\
\cellcolor{gray!6}{Asian} & \cellcolor{gray!6}{\num{-0.294}} & \cellcolor{gray!6}{\num{-0.566}} & \cellcolor{gray!6}{\num{-2.496}**} & \cellcolor{gray!6}{\num{-0.568}} & \cellcolor{gray!6}{\num{0.634}}\\
Hispanic or Latino/x & \num{0.324} & \num{0.116} & \num{0.529}* & \num{0.632}** & \num{-0.585}*\\
\cellcolor{gray!6}{Num.Obs.} & \cellcolor{gray!6}{\num{948}} & \cellcolor{gray!6}{\num{948}} & \cellcolor{gray!6}{\num{948}} & \cellcolor{gray!6}{\num{948}} & \cellcolor{gray!6}{\num{948}}\\
\midrule
$R_{McFadden}^2$ & \num{0.193} & \num{0.121} & \num{0.145} & \num{0.154} & \num{0.221}\\
\cellcolor{gray!6}{BIC} & \cellcolor{gray!6}{\num{1152.2}} & \cellcolor{gray!6}{\num{1237.6}} & \cellcolor{gray!6}{\num{1048.0}} & \cellcolor{gray!6}{\num{864.8}} & \cellcolor{gray!6}{\num{1104.6}}\\
Log.Lik. & \num{-524.709} & \num{-567.376} & \num{-472.576} & \num{-380.971} & \num{-500.907}\\
\bottomrule
\multicolumn{6}{l}{\rule{0pt}{1em}* p $<$ .05. ** p $<$ .01. *** p $<$ .001 (two-tailed test).}\\
\multicolumn{6}{l}{\rule{0pt}{1em}Raw, Unexponentiated Coefficients}\\
\end{tabular}}
\end{table}

>>>>

\begin{sidewaystable}
\caption{\label{tab:table-model-2}What predicts someone intentionally searched for information, by vehicle of information search}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}{llllll}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{5}{c}{Dependent Variable} \\
\cmidrule(l{3pt}r{3pt}){2-6}
  & Doctor & Person & Online Forum & Social Networking Site & Online Search\\
\midrule
\cellcolor{gray!6}{Received Info, Doctor} & \cellcolor{gray!6}{\num{1.942}***} & \cellcolor{gray!6}{\num{1.124}***} & \cellcolor{gray!6}{\num{0.181}} & \cellcolor{gray!6}{\num{0.540}**} & \cellcolor{gray!6}{\num{0.430}**}\\
Received Info, Person & \num{0.800}*** & \num{1.199}*** & \num{0.728}*** & \num{0.281} & \num{0.365}*\\
\cellcolor{gray!6}{Received Info, News} & \cellcolor{gray!6}{\num{0.437}**} & \cellcolor{gray!6}{\num{0.100}} & \cellcolor{gray!6}{\num{0.359}*} & \cellcolor{gray!6}{\num{0.514}*} & \cellcolor{gray!6}{\num{1.091}***}\\
Received Info, Social Networking Site & \num{-0.130} & \num{0.437}** & \num{-0.603}** & \num{0.731}*** & \num{1.272}***\\
\cellcolor{gray!6}{Received Info, Online Forum} & \cellcolor{gray!6}{\num{0.412}*} & \cellcolor{gray!6}{\num{0.263}+} & \cellcolor{gray!6}{\num{1.266}***} & \cellcolor{gray!6}{\num{0.974}***} & \cellcolor{gray!6}{\num{0.695}***}\\
Age & \num{0.002} & \num{0.001} & \num{-0.007} & \num{-0.003} & \num{0.029}***\\
\cellcolor{gray!6}{Gender, Male} &\cellcolor{gray!6}{\num{0.100}} & \cellcolor{gray!6}{\num{-0.124}} & \cellcolor{gray!6}{\num{0.070}} & \cellcolor{gray!6}{\num{-0.075}} & \cellcolor{gray!6}{\num{-0.147}}\\
Gender, Other & \num{-1.078} &\num{-1.307} & \num{-13.953} & \num{-12.740} & \num{-0.954}\\
\cellcolor{gray!6}{Associate's Deg or above} & \cellcolor{gray!6}{\num{0.542}**} & \cellcolor{gray!6}{\num{0.154}} & \cellcolor{gray!6}{\num{1.086}***} & \cellcolor{gray!6}{\num{1.344}***} & \cellcolor{gray!6}{\num{-0.952}***}\\
White & \num{0.631} & \num{0.245} & \num{0.009} & \num{0.559} & \num{0.012}\\
\cellcolor{gray!6}{Black} & \cellcolor{gray!6}{\num{0.366}} & \cellcolor{gray!6}{\num{0.208}} & \cellcolor{gray!6}{\num{0.608}} & \cellcolor{gray!6}{\num{0.646}} & \cellcolor{gray!6}{\num{0.357}}\\
Native American & \num{0.309} & \num{-0.696} & \num{0.209} & \num{0.762} & \num{-0.831}\\
\cellcolor{gray!6}{Asian} & \cellcolor{gray!6}{\num{-0.294}} & \cellcolor{gray!6}{\num{-0.566}} & \cellcolor{gray!6}{\num{-2.496}**} & \cellcolor{gray!6}{\num{-0.568}} & \cellcolor{gray!6}{\num{0.634}}\\
Hispanic or Latino/x & \num{0.324} & \num{0.116} & \num{0.529}* & \num{0.632}** & \num{-0.585}*\\
\cellcolor{gray!6}{Num.Obs.} & \cellcolor{gray!6}{\num{948}} & \cellcolor{gray!6}{\num{948}} & \cellcolor{gray!6}{\num{948}} & \cellcolor{gray!6}{\num{948}} & \cellcolor{gray!6}{\num{948}}\\
\midrule
$R_{McFadden}^2$ & \num{0.193} & \num{0.121} & \num{0.145} & \num{0.154} & \num{0.221}\\
\bottomrule
\multicolumn{6}{l}{\rule{0pt}{1em}* p $<$ .05. ** p $<$ .01. *** p $<$ .001 (two-tailed test).}\\
\multicolumn{6}{l}{\rule{0pt}{1em}Raw, Unexponentiated Coefficients}\\
\end{tabular}}
\end{sidewaystable}
